State of the Practice for Medical Imaging Software

### 2022-11-02 StateOfPractice/Papers/MedImageSoft_SOP/MedImageSoft_SOP.tex
Anonymized version of the SOP for MI paper

%\documentclass[preprint,12pt,authoryear]{elsarticle}
%\documentclass[3p, 12pt,authoryear]{elsarticle}
\documentclass[final, 3p, times, authoryear]{elsarticle}

@@

\journal{Academic Radiology}

@@

	\item \textbf{Usability} ``The extent to which a product can be used by
	specified users to achieve specified goals with effectiveness, efficiency,
	and satisfaction in a specified context of use'' \citep{ISO/TR16982:2002}
	\citep{ISO9241-11:2018}.

	\item \textbf{Maintainability} The effort with which a software system or
	component can be modified to i) correct faults; ii) improve performance or
	other attributes; iii) satisfy new requirements
	\citep{IEEEStdGlossarySET1990}, \citep{boehm2007software}.

@@

Domain experts may be recruited from academia or industry.  The only
requirements are knowledge of the domain and a willingness to be engaged in the
assessment process.  The Domain Expert does not have to be a software developer,
but they should be a user of domain software.  Given that the domain experts are
likely to be busy people, the measurement process cannot put too much of a burden
on their time.  For the current assessment, our Domain Expert (and paper
co-author) is Dr.\ Michael Noseworthy, Professor of Electrical and Computer
Engineering at McMaster University, Co-Director of the McMaster School of
Biomedical Engineering, and Director of Medical Imaging Physics and Engineering
at St.\ Joseph's Healthcare, Hamilton, Ontario, Canada.

@@

We based our interviews on a list of 20 questions, which can be found in
\citet{SmithEtAl2021}. Some questions are about the background of the software,
the development teams, the interviewees, and how they organize their projects.
We also ask about the developer's understanding of the users. Some questions
focus on the current and past difficulties, and the solutions the team has
found, or plan to try. We also discuss documentation, both with respect to how
it is currently done, and how it is perceived. A few questions are about
specific software qualities, such as maintainability, understandability,
usability, and reproducibility. The interviews are semi-structured based on the
question list; we ask follow-up questions when necessary.  The interview process
presented here was approved by the McMaster University Research Ethics Board
under the application number 
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/MACREM/Application.pdf}
{MREB\#: 5219}.

@@

Figure~\ref{fg_maintainability_scores} shows the ranking results for
maintainability. We gave \textit{3D Slicer} the highest score because we found
it to have the most comprehensive artifacts. For example, as far as we could
find, only a few of the 29 projects had a product, developer's manual, or API
documentation, and only \textit{3D Slicer}, \textit{ImageJ}, \textit{Fiji}
included all three documents. Moreover, \textit{3D Slicer} has a much higher
percentage of closed issues (91.65\%) compared to \textit{ImageJ} (52.49\%) and
\textit{Fiji} (63.79\%). Table~\ref{tab_maintainability_docs} shows which
projects had these documents, in descending order of their maintainability
scores.

@@

%% Bibliography
\bibliographystyle{ACM-Reference-Format}
\bibliography{MedImageSoft_SOP}

>>>>

%\documentclass[preprint,12pt,authoryear]{elsarticle}
%\documentclass[3p, 12pt,authoryear]{elsarticle}
\documentclass[final, 3p, times, authoryear, doubleblind]{elsarticle}

@@

\journal{Archives of Computational Methods in Engineering}

@@

	\item \textbf{Usability} ``The extent to which a product can be used by
	specified users to achieve specified goals with effectiveness, efficiency,
	and satisfaction in a specified context of use'' \citep{ISO/TR16982:2002,
	ISO9241-11:2018}.

	\item \textbf{Maintainability} The effort with which a software system or
	component can be modified to i) correct faults; ii) improve performance or
	other attributes; iii) satisfy new requirements
	\citep{IEEEStdGlossarySET1990, boehm2007software}.

@@

Domain experts may be recruited from academia or industry.  The only
requirements are knowledge of the domain and a willingness to be engaged in the
assessment process.  The Domain Expert does not have to be a software developer,
but they should be a user of domain software.  Given that the domain experts are
likely to be busy people, the measurement process cannot put too much of a burden
on their time.  For the current assessment, our Domain Expert (and paper
co-author) is Anonymous % DOUBLE BLIND
% Dr.\ Michael Noseworthy, Professor of Electrical and Computer
% Engineering at McMaster University, Co-Director of the McMaster School of
% Biomedical Engineering, and Director of Medical Imaging Physics and Engineering
% at St.\ Joseph's Healthcare, Hamilton, Ontario, Canada.

@@

We based our interviews on a list of 20 questions, which can be found in
\citet{SmithEtAl2021}. Some questions are about the background of the software,
the development teams, the interviewees, and how they organize their projects.
We also ask about the developer's understanding of the users. Some questions
focus on the current and past difficulties, and the solutions the team has
found, or plan to try. We also discuss documentation, both with respect to how
it is currently done, and how it is perceived. A few questions are about
specific software qualities, such as maintainability, understandability,
usability, and reproducibility. The interviews are semi-structured based on the
question list; we ask follow-up questions when necessary.  The interview process
presented here was approved by the Anonymous Ethics Board. %% DOUBLE BLIND
% McMaster University Research Ethics Board
% under the application number 
% \href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/MACREM/Application.pdf}
% {MREB\#: 5219}.

@@

Figure~\ref{fg_maintainability_scores} shows the ranking results for
maintainability. We gave \textit{3D Slicer} the highest score because we found
it to have the most comprehensive artifacts. For example, as far as we could
find, only a few of the 29 projects had a product, developer's manual, or API
documentation, and only \textit{3D Slicer}, \textit{ImageJ}, \textit{Fiji}
included all three documents. Moreover, \textit{3D Slicer} has a much higher
percentage of closed issues (92\%) compared to \textit{ImageJ} (52\%) and
\textit{Fiji} (64\%). Table~\ref{tab_maintainability_docs} shows which
projects had these documents, in descending order of their maintainability
scores.

@@

%% Bibliography
\bibliographystyle{ACM-Reference-Format}
%\bibliography{MedImageSoft_SOP}
\bibliography{MedImageSoft_SOP_Anonymous}
